---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/StatsWithR/statsr.svg?branch=BayesFactor)](https://travis-ci.org/StatsWithR/statsr)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/statsr)](https://cran.r-project.org/package=statsr)
[![](https://cranlogs.r-pkg.org/badges/statsr)](https://CRAN.R-project.org/package=statsr) [![](https://cranlogs.r-pkg.org/badges/grand-total/statsr)](https://CRAN.R-project.org/package=statsr)

# statsr

The `R` package `statsr` provides functions and datasets to support the Coursera [*Statistics with `R` Specialization*](https://www.coursera.org/specializations/statistics)  videos and open access book
[*An Introduction to Bayesian Thinking*](https://statswithr.github.io/book) for learning Bayesian and freqentist statistics using `R`. 


To install the latest version from github, verify that there is a passing badge above on the README page.  In `R` enter

```{r github, echo=TRUE,eval=FALSE}
library(devtools)
devtools::install_github("statswithr/statsr",
                         dependencies=TRUE,
                         upgrade_dependencies = TRUE)
```

This will install the packages and any packages that are required, as well as updating any installed packages to their latest versions.
